Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-05-17 paper/IJCAI19/paper.tex
folders structure

The dataset and tools (Lithium slicer and \comb{}) will be made
available once double-blind requirements are lifted.

@@

This material is based upon work supported by Fundação para a Ciência 
e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017. The work 
reported in this article was supported by national funds through Fundação 
para a Ciência e a Tecnologia (FCT) with reference UID/CEC/50021/2019.

>>>>

@@

This material is based upon work supported by Fundação para a Ciência 
e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017. The work
reported in this article was supported by national funds through Fundação
para a Ciência e a Tecnologia (FCT) with reference UID/CEC/50021/2019.
